% ----------------------------------------------------
% Housing Subsystem
% ----------------------------------------------------
\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\input{../FrontMatter/Glossary.tex}
\begin{document}
	% ----------------------------------------------------
	\chapter{Housing Subsystem (VSTMIC004)}
	\vspace{0.5cm}
	% ---------------------------------------------------
	\section{Introduction}
	The aim of this subsection is to discuss the design and implementation of the housing of the final design. This housing will physically contain and protect all other subsystems as well as facilitate their operation.
	
	\section{Requirement Analysis}
	
	\begin{table}
		\centering
		\caption{Functional Specifications of the Housing Subsystem}
		\label{tab:H1}
		\begin{tabular}{|1|1|1|}
			\hline
			\textbf{User   Requirement} & \textbf{Specification   Description}                                                                                                                                           & \textbf{Specification   no.} \\ \hline
			Portable                    & The final internal size of the design must be 100x100x50mmz                                                                                                                     & HS1                          \\ \hline 
			Weight Capacity             & \begin{tabular}[c]{@{}l@{}}The final design must be able to support the weight of all other subsystems including\\  the maximum weight of the scale.\end{tabular}                                                         & HS2                          \\ \hline
			Weight Distribution         & \begin{tabular}[c]{@{}l@{}}The final design must be able to contain all other subsystems in such a way that\\  the overall center of gravity of the final design sits in the middle of the housing subsystem\end{tabular} & HS3                          \\ \hline 
			External Push Button        & \begin{tabular}[c]{@{}l@{}}The housing must support an external push button that can directly interface with\\  the tare function developed in the Sensing Subsection\end{tabular}                                        & HS4                           \\ \hline
		\end{tabular}
	\end{table}

\section{Design Process}
\subsection{Housing Sections}
The sections that will make up the housing subsystem can be broadly categorized into two sections; the outer section and the inner section. The outer section will directly interface with the users while the inner section will interface and house the other subsections. 

The outer section will need to comply not only with all the user requirements but will also need to comply with any further material considerations, as will be discussed in section [next]. The outer section will directly interact with specifications HS1, HS2, HS3 and HS4.

The internal section will primarily govern the HS3 specification as it will determine how the other subsections will be contained within the final housing. It will need to distribute the weight of all other subsections such that the accuracy of the sensing subsection is not affected.

\subsection{Material Requirements}
As emphasized during the literature review, material choice is a component that is of particular importance regarding this subsection. Not only is material choice a variable in the execution of the user requirements, but it is important to choose materials that won’t harm or pose any danger to the wildlife that will be interacting with the final design. From the research conducted in the literature review, the following material specifications have been designated,

\begin{table}[]
	\caption{Material Requirements}
	\label{tab:h2}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Material requirement} & \textbf{Requirement Description}                                                                                                                                                                                                                                              & \textbf{Requirement No.} \\ \hline
		Avian-safe                    & \begin{tabular}[c]{@{}l@{}}The materials used should not be toxic in any way towards avian species. The \\ materials used should not have any sharp edges or corners that can harm avians that\\  will be interacting with the final design.\end{tabular}                     & HSM1                     \\ \hline
		User-safe                     & \begin{tabular}[c]{@{}l@{}}The materials used should not be toxic in any to the users that will interact with \\ the final design. The materials used should not have any sharp edges or corners\\ that can harm users that will interact with the final design.\end{tabular} & HSM2                     \\ \hline
		Density Consistency           & \begin{tabular}[c]{@{}l@{}}The materials chosen should be evenly dense such that the center of gravity of \\ the final housing design lies equidistant between all edges of the outer section\end{tabular}                                                                    & HSM3                     \\ \hline
		Ease of Modularity            & \begin{tabular}[c]{@{}l@{}}The materials chosen must be easy to modify (either permanent or temporary \\ modifications) by both the designers of the subsection and end users.\end{tabular}                                                                                   & HSM4                     \\ \hline
		Environmental Resistance      & \begin{tabular}[c]{@{}l@{}}The materials chosen should be able to resist damage from water and sunlight \\ such that, even if prolonged for long periods of time, the functionality of every \\ subsection (including this one) remains unaffected.\end{tabular}              & HSM5                     \\ \hline
		Budget Constraint             & \begin{tabular}[c]{@{}l@{}}The total cost of all the materials require should fall within the budget for the \\ entire subsection (R450)\end{tabular}                                                                                                                         & HSM6                     \\ \hline
	\end{tabular}
\end{table}

\subsection{Material Options}
After going over all of the information obtained in the literature review, a common through-line is that synthetic materials and metals tend to raise the most concern regarding avian toxicity. Metals, especially thinner pieces, would struggle adhering to each other without the use of solder or welding as they will be too thin to be screwed together. This is especially cause for concern as direct contact with solder or any lead-based adhesive will direct lead to avian toxicity. Taking all of this into account, all materials that will be considered will be wooden or wood-based. This way we can insure all user requirements are met.
Taking into account all viable materials available at local hardware stores, the following list has been compiled alongside all material requirements they fulfill. The following list includes the associated product code at BuCo as of 2024/05/12. From this list, materials that fulfill all requirements will be analyzed further based on their cost-effectiveness.

\begin{table}[]
	\caption{Material Analysis}
	\label{tab:H3}
	\begin{tabular}{llll}
		\textbf{Product Type}   & \textbf{BuCo SKU} & \textbf{Requirements Fulfilled} & \textbf{Requirement Discussion}                                                                                                                                                                                                                                                                                                  \\
		Plywood                 & 1274706           & HSM1,HSM2,HSM3,HSM4, HSM5, HSM6 & Fulfills all material requirements                                                                                                                                                                                                                                                                                               \\
		Hardboard               & 1292581           & HSM1, HSM2, HSM3, HSM4, HSM6    & \begin{tabular}[c]{@{}l@{}}Does not fulfill the HSM5 requirement \\ as it has little moisture resistance.\end{tabular}                                                                                                                                                                                                           \\
		Chipboard               & 1283947           & HSM1, HSM2, HSM3, HSM6          & \begin{tabular}[c]{@{}l@{}}Does not fulfill the HSM4 requirement as it \\ cannot be altered easily without the use of \\ adhesives, which will compromise the \\ structural integrity of the housing design. \\ It also does not meet the HSM5 \\ requirement due to its tendency to chip \\ and shatter over time.\end{tabular} \\
		SupaWood                & 1276088           & HSM1,HSM2,HSM3,HSM4, HSM5, HSM6 & Fulfills all material requirements.                                                                                                                                                                                                                                                                                              \\
		Laminated Pine Shelving & 1124588           & HSM1,HSM2,HSM3,HSM4, HSM5       & \begin{tabular}[c]{@{}l@{}}Does not fulfill the HSM6 requirement due\\  to it being outside of the subsystem budget.\end{tabular}                                                                                                                                                                                               
	\end{tabular}
\end{table}

From the above list the two most viable materials, including their sizing and pricing, are cataloged below,

	\begin{table}
	\centering
	\caption{Furthered Material Analysis}
	\label{tab:H4}
	\begin{tabular}{|1|1|1|}
		\hline
		\textbf{Product Type} & \textbf{Dimensions (mm)} & \textbf{Pricing} &  \\ \hline
		Plywood               & 2440x1220x3.6            & R426.98          &  \\ \hline
		SupaWood              & 2750x1830x3              & R302. 02         &   \\ \hline
	\end{tabular}
\end{table}

Taking into consideration the amount of raw material obtained for the price, SupaWood will be selected as the primary material of choice for both the outer and internal sections of the housing.

\subsection{Housing Layout}
The outer section will be designed alongside the internal section of the housing to ensure that they interface properly. The outer section will consist of a 110x110x3mm sheet of SupaWood. This will serve as a platform for the birds to stand on top of while their measurements are being taken. The load cell will be connected on the underside of it in the center. The Internal section of the housing will consist of a 100x100x3mm sheet of SupaWood with four 2x100x3mm slabs of SupaWood attached on each edge. This will ensure that all internal components will be fixed in place and protected from environmental conditions. The load cell will be connected to the top of the internal section and hence connects the internal and outer sections of the housing together. 

\section{Acceptance Test Procedures and Quality Assessment}
It is vital that we test the housing subsystem and ensure its quality to ensure that it will not negatively affect any other subsystem. It is also vital that the housing complies to all requirements. If the housing fails any of the listed requirements, then it will end up negatively affecting the end user and will make the entire design unreliable. 

The portability requirement (HS1) is achieved and validated during the layout design stage of the subsystem. With both sections of the layout connected, the entire design will still comply with the specified range of 110x110x50mm. This will ensure that the entire system, including all subsystems and internal components, remain portable and easy to use for the end user.

The weight capacity requirement (HS2) is directly related to the material choice of the housing. As we decided on using SupaWood, which can support weights far greater than the maximum rating of the final design (500g), the housing will be able to support not only the weight of itself but also any weight that will be placed on the scale.

The weight distribution requirement (HS3) is primarily governed by the material choice and housing layout. The layout was designed in such a way that the weight of all internal components and subsystems do not place any external strain on the load cell. This leads to the entire system remaining intrinsically balanced in such a way to ensure accuracy of the sensing subsystem. The material choice also reinforces this, as it was chosen specifically for its low tolerance for density variation.

The external push button requirement (HS4) is easily implemented as the push button can directly be connected to the internal section of the housing without placing any loading or external strain on the load cell while in use. The inclusion of a push button will also not impede on any other requirements, due to the nature of the layout. 

\section{Conclusion}
In conclusion, through an iterative and analytical design process, a viable housing system was developed. The purpose of this housing is vital to the overall design, as it facilitates the operation of all other subsystems. This housing also ensures that the final design is portable and easy to interface with for the end user. Many materials were considered during the designing of the housing and after consulting several studies the importance of natural materials for this application were made explicit. The final material choice complies with all material requirements laid out and facilitates the ease of execution of the acceptance test procedures. All of these factors combined resulted in a housing design that is suitable for real world application. 
% ----------------------------------------------------
	\ifstandalone
	\bibliography{../Bibliography/References.bib}
	\printnoidxglossary[type=\acronymtype,nonumberlist]
	\fi
	
\end{document}
% ----------------------------------------------------

